Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
more formatting statistical results

			Chi\^2	2-tail p	Sig?		n		effect size \\
Friends-Work	20.365	<0.0001	Yes		5039		0.004\\
Friends-Public	5.349	0.0207	No		5146		0.001\\
Friends-App	380.000	<0.0001	Yes		5098		0.075\\
Work-Public	5.054	0.0246	No		5133		0.001\\
Work-App		564.318	<0.0001	Yes		5085		0.111\\
Public-App		479.980	<0.0001	Yes		5192		0.092\\

Friends-Work	0.867	0.3517	No		604		0.001\\
Friends-Public	1.460	0.2229	No		639		0.002\\
Friends-App	32.066	<0.0001	Yes		609		0.053\\
Work-Public	0.670	0.7956	No		631		0.001\\
Work-App		42.492	<0.0001	Yes		601		0.071\\
Public-App		48.520	<0.0001	Yes		636		0.076\\

@@

For shared data (friends, work, public) \\[-.8cm]

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  %\setcounter{enumi}{0}
  \item social security number (98.04\%)
  \item a video of you unclothed (97.44\%)
  \item bank account information (97.10\%)
  \item recordings of your work conversations (96.97\%)
  \item a photo of you that is incriminating/embarrassing (96.36\%)
  \item a photo of you unclothed (96.30\%)
  \item credit card information (95.92\%)
  \item username and password for websites (95.41\%)
  \item a video of you entering in your PIN (93.91\%)
  \item recordings of your phone conversations (93.88\%) \\[-.8cm]
\end{enumerate}

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  \setcounter{enumi}{63}
  \item your name (47.25\%)
  \item when and how much you exercise (46.07\%)
  \item when you were happy or having fun (38.10\%)
  \item what television shows you watch (35.96\%)
  \item when you are busy or interruptible (34.34\%)
  \item your heart rate (32.28\%)
  \item music from your device (31.87\%)
  \item your age (29.67\%)
  \item the language you speak (20.95\%)
  \item your gender (16.81\%) \\[-.8cm]
\end{enumerate}

For not shared data (appserver only)  \\[-.8cm]

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  %\setcounter{enumi}{0}
  \item bank account information (90.91\%)
  \item a video of you unclothed (90.62\%)
  \item social security number (88.68\%)
  \item video of you entering your PIN (88.57\%)
  \item a photo of you that is incriminating/embarrassing (78.05\%)
  \item a photo of you unclothed (77.78\%)
  \item a video of you entering a passcode to a door (75.00\%)
  \item when and how much you have sex (73.08\%)
  \item a video of you that is incriminating/embarrassing (71.88\%)
  \item a photo of you at home taken randomly by an inward-facing camera (66.67\%)  \\[-.8cm]
\end{enumerate}

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  \setcounter{enumi}{63}
  \item when and how much you exercise (16.67\%)
  \item how much you use your phone (15.79\%)
  \item your age (14.29\%)
  \item how much you like the people you interact with (13.79\%)
  \item when, what, and how much you ate (12.50\%)
  \item which television shows you watch (11.43\%)
  \item your gender (9.52\%)
  \item your heart rate (9.09\%)
  \item eye movement patterns (for eye tracking) (6.98\%)
  \item the language you speak (2.50\%)\\[-.8cm]
\end{enumerate}

>>>>

%\begin{table}%[h]
%\begin{center}
%\begin{tabular}{llllll}
%Recipients	& Chi^2 &	2-tail P & 	Sig?	& n & Effect Size \\
%Work-App	& 564.318 & <0.0001 & Yes	& 5085 & 0.111\\
%Public-App	& 479.980 & <0.0001 & Yes	& 5192 & 0.092\\
%Friends-App & 380.000 & <0.0001 & Yes & 5098 & 0.075\\
%Friends-Work & 20.365 & <0.0001 & Yes & 5039 & 0.004\\
%Friends-Public & 5.349 & 0.0207 & No	& 5146 & 0.001\\
%Work-Public&  5.054 & 0.0246 & No & 5133	& 0.001\\
%\end{tabular}
%\caption{Results of a Chi-Squared test of the effects of various recipients contributing to VUR.}
%\label{recipient}
%\end{center}
%\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{llll}
Recipients	& Chi^2 &	2-tail P &  Effect Size \\
Work-App	& 564.318 & <0.0001 & 0.111\\
Public-App	& 479.980 & <0.0001 &  0.092\\
Friends-App & 380.000 & <0.0001 & 0.075\\
Friends-Work & 20.365 & <0.0001 &  0.004\\
Friends-Public & 5.349 & 0.0207 &  0.001\\
Work-Public&  5.054 & 0.0246 &  0.001\\
\end{tabular}
\caption{Results of a Chi-Squared test of the effects of various recipients contributing to VUR.}
\label{recipient}
\end{center}
\end{table}

%Friends-Work	0.867	0.3517	No		604		0.001\\
%Friends-Public	1.460	0.2229	No		639		0.002\\
%Friends-App	32.066	<0.0001	Yes		609		0.053\\
%Work-Public	0.670	0.7956	No		631		0.001\\
%Work-App	42.492	<0.0001	Yes		601		0.071\\
%Public-App	48.520	<0.0001	Yes		636		0.076\\

@@

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
<data> & VUR  \\
social security number & 98.04\% \\
a video of you unclothed & 97.44\% \\
bank account information & 97.10\% \\
recordings of your work conversations & 96.97\% \\
an incriminating/embarrassing photo of you & 96.36\% \\
a photo of you unclothed & 96.30\% \\
credit card information & 95.92\% \\
username and password for websites & 95.41\% \\
a video of you entering in your PIN & 93.91\% \\
recordings of your phone conversations & 93.88\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
%starting from #63
<data> &  VUR  \\
bank account information & 90.91\% \\
a video of you unclothed & 90.62\% \\
social security number  & 88.68\% \\
video of you entering your PIN & 88.57\% \\
an incriminating/embarrassing photo of you & 78.05\% \\
a photo of you unclothed & 77.78\% \\
a video of you entering a passcode to a door & 75.00\% \\
when and how much you have sex & 73.08\% \\
an incriminating/embarrassing video of you & 71.88\% \\
a random (inward-facing) photo of you at home & 66.67\% \\
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedtop10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
%starting from #63
<data> &  VUR  \\
your name & 47.25\% \\
when and how much you exercise & 46.07\% \\
when you were happy or having fun & 38.10\% \\
what television shows you watch & 35.96\% \\
when you are busy or interruptible & 34.34\% \\
your heart rate & 32.28\% \\
music from your device & 31.87\% \\
your age & 29.67\% \\
the language you speak & 20.95\% \\
your gender & 16.81\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
\label{sharedbottom10}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{ll}
%starting from #63
<data> &  VUR  \\
when and how much you exercise & 16.67\% \\
how much you use your phone & 15.79\% \\
your age & 14.29\% \\
how much you like the people you interact with & 13.79\% \\
when, what, and how much you ate & 12.50\% \\
which television shows you watch & 11.43\% \\
your gender & 9.52\% \\
your heart rate & 9.09\% \\
eye movement patterns (for eye tracking) & 6.98\% \\
the language you speak & 2.50\% \\
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{notsharedbottom10}
\end{center}
\end{table}
